upwell_IDX

### 2019-11-29 upwell_IDX.Rmd
new laptop commit

```{r}
library(circular)
devtools::install_github("robwschlegel/coastR")
library(gridExtra)
library(geosphere)
library(tidyverse)
library(heatwaveR)
library(coastR)
```

>>>>

```{r}
# Installling andloading libraries

library(circular)
## devtools::install_github("robwschlegel/coastR")
library(gridExtra)
library(geosphere)
library(tidyverse)
library(heatwaveR)
library(coastR)
```
